Incentivizing Exploration with Unbiased History

### 2018-11-02 2level.tex
Minor edit in figure.
Moved the assn back to prelims.

\begin{figure}[H]
\centering
\begin{tikzpicture}
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw(2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw(3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw(9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \fdpL$ rounds};
  \node at(0.5,0.5){$\fdpL$};
  \node at(1.5,0.5){$\fdpL$};
  \node at(2.5,0.5){$\fdpL$};
  \node at(3.5,0.5){$\fdpL$};
  \node at(9.5,0.5){$\fdpL$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

@@

The proofs can be found in Appendix~\ref{app:warmup}. To simplify presentation, here and elsewhere we make the following assumption (which can be removed at the cost of a somewhat lengthier proofs).

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to the same \emph{estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
\end{assumption}

Among other things, this assumption allows us to the define the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths. Then,

>>>>

\begin{figure}[H]
\centering
\begin{tikzpicture}
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw(2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw(3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw(9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){all remaining rounds};
  \node at(0.5,0.5){$\fdpL$};
  \node at(1.5,0.5){$\fdpL$};
  \node at(2.5,0.5){$\fdpL$};
  \node at(3.5,0.5){$\fdpL$};
  \node at(9.5,0.5){$\fdpL$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

@@

The proofs can be found in Appendix~\ref{app:warmup}. One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths. Then,

### 2018-11-02 model.tex
some edit.
Moved the assn back to prelims.

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}
\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.

@@

We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average. Formally, the model is characterized by the following assumption (which we make without further notice).

@@

>>>>

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}

@@

We allow a much more permissive model that allows agents to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average. Formally, the model is characterized by the following assumptions (which we make without further notice).

@@

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to an \emph{estimate function} $f_t$ from anonymized subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
\end{assumption}
